### 2017-07-14 eugene_notes.tex
better way of getting load

\newcommand{\mL}{\mathcal{L}}
\newcommand{\ip}[2]{\langle #1, #2 \rangle}

@@

Take $\mu(x) = ax^2$.
The mean fitness in the population is then
$$\begin{aligned}
    \ip{1/(1+\mu)}{X}
    &=
    \ip{1 - ax^2 + a^2 x^4}{X} + O(a^3) \\
    &=
    1 - a m_2 + a^2 m_4 + O(a^3) \\
    &=
    1 - 2 a \eta^2 + 6 a^2 \eta^4 + O(a^3) ,
\end{aligned}$$
and the mean fitness of \emph{offspring} is
$$\begin{aligned}
    \ip{1/(1+\mu)}{\nu(X)}
    &=
    \ip{1 - ax^2 + a^2 x^4}{\nu(X)} + O(a^3) \\
    &=
    1 - a \left( \frac{m_2}{2} + \eta^2 \right) 
        + a^2 \left( 2 m_4 + 6 m_2^2 + 12 m_2 \eta^2 + 3 \eta^4\right) + O(a^3) \\
    &=
    1 - a \left( 2 \eta^2 - a \eta^4 \right)
        + a^2 \left( 8 \eta^4 + 24 \eta^4 + 24 \eta^4 + 3 \eta^4\right) + O(a^3) \\
    &=
    1 - 2 a \eta^2 + 60 a^2 \eta^4 + O(a^3) .
\end{aligned}$$
This implies that the difference in mean fitness between parents and offspring
(maybe this is called recombination load?)
is $54 a^2 \eta^4 + O(a^3)$.
(SOMETHING IS WRONG here because mean fitness in offspring should be less than in parents).

>>>>

\newcommand{\mL}{\mathcal{L}}
\newcommand{\ip}[2]{\left\langle #1, #2 \right\rangle}

@@

Since $\nu(X)$ is the offspring distribution,
and we know that $\nu(X) = (1+\mu) X / \ip{1+\mu}{X}$,
we can compute mean fitness of offspring as
$$\begin{aligned}
    \ip{\frac{1}{1+\mu}}{\nu(X)}
    &=
    \frac{\ip{\frac{1}{1+\mu}}{(1+\mu)X}}{\ip{1+\mu}{X}} \\
    &=
    \frac{1}{\ip{1+\mu}{X}} .
\end{aligned}$$

Take $\mu(x) = ax^2$.
The mean fitness in the population is then
$$\begin{aligned}
    \ip{1/(1+\mu)}{X}
    &=
    \ip{1 - ax^2 + a^2 x^4}{X} + O(a^3) \\
    &=
    1 - a m_2 + a^2 m_4 + O(a^3) \\
    &=
    1 - 2 a \eta^2 + 6 a^2 \eta^4 + O(a^3) ,
\end{aligned}$$
and the mean fitness among offspring is
$$\begin{aligned}
    \frac{1}{1+am_2} 
    &= 1 - 2 a \eta^2 + 2 a^2 \eta^4 + O(a^3),
\end{aligned}$$
so the difference in mean fitness between parents and offspring
(maybe this is called recombination load?)
is $4 a^2 \eta^4$.

Here is the same thing calculated the other way,
but something is wrong:
The mean fitness of offspring is
$$\begin{aligned}
    \ip{1/(1+\mu)}{\nu(X)}
    &=
    \ip{1 - ax^2 + a^2 x^4}{\nu(X)} + O(a^3) \\
    &=
    1 - a \left( \frac{m_2}{2} + \eta^2 \right) 
        + a^2 \left( 2 m_4 + 6 m_2^2 + 12 m_2 \eta^2 + 3 \eta^4\right) + O(a^3) \\
    &=
    1 - a \left( 2 \eta^2 - a \eta^4 \right)
        + a^2 \left( 8 \eta^4 + 24 \eta^4 + 24 \eta^4 + 3 \eta^4\right) + O(a^3) \\
    &=
    1 - 2 a \eta^2 + 60 a^2 \eta^4 + O(a^3) .
\end{aligned}$$
The difference here is
is $54 a^2 \eta^4 + O(a^3)$.
(something is wrong here because mean fitness in offspring should be less than in parents).
